### 2022-12-05 Manuscript.qmd
revision

---
title: "Managing Fungal Infections in the Era of Targeted Therapy for Acute Myelogenous Leukemia"
format: html
editor: visual
bibliography: references.bib
csl: clinical-infectious-diseases.csl
---

Russell E. Lewis, Pharm.D., Associate Professor of Medicine, Infectious Diseases^1^

Marta Stanzani, M.D., Ph.D.^2^ Deparmtnet of Hematology

^1^Department of Molecular Medicine, University of Padua, Padua Italy

^2^Department of Hematology, Cá Funcello Hospital, USL2 Treviso, Italy

## Abstract

## Introduction

### 2022-12-06 Manuscript.qmd
revision

@@
 
-Russell E. Lewis, Pharm.D., Associate Professor of Medicine, Infectious Diseases^1^
+Russell E. Lewis, Pharm.D.^1^
 
-Marta Stanzani, M.D., Ph.D.^2^ Deparmtnet of Hematology
+Marta Stanzani, M.D., Ph.D.^2^
 
-^1^Department of Molecular Medicine, University of Padua, Padua Italy
+^1^Associate Professor of Medicine, Department of Molecular Medicine, University of Padua, Padua, Italy:ORCID ID:
 
-^2^Department of Hematology, Cá Funcello Hospital, USL2 Treviso, Italy
+^2^Director of Hematopoietic Stem Cell Transplantation and Cellular Therapy,   Hematology Unit, Ca' Foncello Hospital,  AULSS 2- Marca Trevigiana, Treviso, Italy:ORCID ID:
+
+##
+
+Keywords
+
+## Competing interests
+
+##
 
@@
 
+15-250 words
+
 ## Introduction
+
+Progress in the understanding of the biology and therapy of acute myeloid leukemia (AML) is evolving at a rapid pace.
+Recent advances in cytogenetics and next-generation sequencing have revealed that AML is a spectrum of clinical-cytogenetic-molecular entities with diverse pathophysiologies requiring different therapies associated with different outcomes [@kantarjian2008].
+This knowledge has fuelled an explosion in the development of novel therapeutics that target abnormal signalling pathways arising from somatic mutations in AML[@newell_cook21].
+Targeted therapies are now increasingly used in combination with, or in place of, traditional cytotoxic chemotherapy [@kantarjian2016].
+Since 2017, nine agents have been approved for various indications in AML [@kantarjian_etal21].
+Several of these agents have been shown to improve survival vs.conventional conventional chemotherapy in selected AML populations, especially among older patients who as little as two decades ago were only offered supportive care, palliation or hospice [@kantarjian_etal22].
+
+Classical induction chemotherapy regimens for AML with combinations of cytarabine and anthracyclines result in prolonged neutropenia that placed the patient at high risk for for developing invasive mold diseases such as aspergillosis [@pagano2016].
+Although improvements in diagnostics and newer antifungal therapies have improved outcomes, average mortality rates 6 weeks after diagnosis still approach 20% [@thompson_young21].
+For those patients who survive the infection, consolidation chemotherapy[@girmenia2014a, @offner1998; @even2011] or progression to hematopoetic stem cell transplantation[@ford_etal21] is often delayed, or eligibility for clinical trials of novel targeted agents may be impacted increasing the risk for relapse and decreased disease-free survival.
+Therefore, prevention or preemeptive control of mold infections is integral for improving the probability of durable remission of the underlying malignancy.
+
+Triazole antifungals
+
+\
+
+**How do targeted therapies alter the risk of invasive mold disease?**
+
+\
+
+**What are the risk with triazole antifungals?**
+
+*Venetoclax*
+
+\
+
+\
+
+FLT3 inhibitors
+
+**What are the risks with echinocandins?**
+
+\
+
+**What are the risk with liposomal amphotericin B?**
+
+\
+
+**What is the promise of future antifungals?**
+
+\
+
+**What is the role of therapeutic drug monitoring?**

### 2022-12-09 Manuscript.qmd
revision

--- 2022-12-05 Manuscript.qmd
@@
 ---
-title: "Managing Fungal Infections in the Era of Targeted Therapy for Acute Myelogenous Leukemia"
+title: "When Precision Therapy Creates Inprecise Choices"
+subtitle: "Antifungal prophyalxis in the era or targeted therapy for acute myelogenoys leukemia"
 format: html
@@
 
-Russell E. Lewis, Pharm.D., Associate Professor of Medicine, Infectious Diseases^1^
+Russell E. Lewis, Pharm.D.^1^
 
-Marta Stanzani, M.D., Ph.D.^2^ Deparmtnet of Hematology
+Marta Stanzani, M.D., Ph.D.^2^
 
-^1^Department of Molecular Medicine, University of Padua, Padua Italy
+^1^Associate Professor of Medicine, Department of Molecular Medicine, University of Padua, Padua, Italy:ORCID ID 000-0002-2002-4339
 
-^2^Department of Hematology, Cá Funcello Hospital, USL2 Treviso, Italy
+^2^Director of Hematopoietic Stem Cell Transplantation and Cellular Therapy,   Hematology Unit, Ca' Foncello Hospital,  AULSS 2- Marca Trevigana, Treviso, Italy:ORCID ID:000-0003-1569-3447
+
+##
+
+## Keywords
+
+## Competing interests
+
+##
 
@@
 
+150-250 words
+
 ## Introduction
+
+Acute myeloid leukemia (AML) is a hematologic malignancy characterized by the proliferation of myeloid blasts or progranulocytes that fail to undergo normal differentiation [@newell_cook21a].
+It is the most common acute leukemia is older adults and historically associated with 5-year survival rates less than 10-15% [@kantarjian_etal21b].
+The standard remission-induction chemotherapy for AML in use for over 40 years combines cytarabine and an anthracycline that results in severe and prolonged neutropenia, which places patients at high risk for developing life-threatening invasive fungal diseases (IFDs) [@taplitz_etal18] Beyond the direct mortality of these infections, IFDs can jeopardize the timing and intensity of subsequent chemotherapy treatment cycles [@girmenia2014a;@even2011] or stem cell transplantation [@cordonnier_etal95;@offner_etal98]increasing the patient's risk for leukemia relapse.
+As a result, antifungal prophylaxis, most commonly with posaconazole, has become a standard of care in many centres to reduce the risk of fungal fungal infection during remission-induction chemotherapy [@maertens_etal18; @cornely2007J]
+
+Progress in the knowledge of the biology and therapy of acute myeloid leukemia (AML) has evolved at a rapid pace over the last two decades.
+High resolution cytogenetics and next-generation sequencing have better defined the molecular drivers or lekemogenesis and disease progression sparking an explosion in novel "targeted thearpies" [@kantarjian2021].
+Most of these new therapies are represented by small molecule kinase inhibitors (SMKIs) that target aberrant signalling pathways that arise form somatic mutations in leukemic cells[@kantarjian_etal21].
+Targeted therapies are now being incorporated in virtually every treatment phase of AML, and increasingly are used in place of more toxic standard chemotherapy regimens in older adults who in the past were only candidates for pallative care or hospise care [@kantarjian_etal22].
+
+Despite the promise of these new therapies, their clinical use in patients with AML is often complicated by drug interactions affecting their metabolic clearance through the CYP3A4/5 pathway [@bruggemann2022] Co-administration of SMKIs with mould-active triazoles such as posaconazole, can result in excessive drug exposures and serious toxicities without dosage adjustment of the SMKIs or discontinuation of the triazole.
+Therefore, clinicians are often faced with the prospect of (i) potentially stopping triazole prophylaxis to avoid interactions with the SMKI; (ii) switching to an alternative antifungal prophylaxis without CYP3A4/5 interactions; (iii) empirically reducing the dose of the SMKI to account for the effect of triazole CYP3A4/5 inhibition; and (iv) continuing both the SMKI and triazole atful dose and monitoring the patient carefully for toxicity.
+Each of these choices are associated with potential risks to patient and must be weighed carefully depending on the treatment setting and resources available for diagnostic testing and therapeutic drug monitoring.
+
+In this review, we address these four questions for the three most common class of prescribed SMKIs-venetoclax, FLT3 inhibitors (midostaurin, gilteritinib, quizartinib) and IDH inhibitors (ivosidenib, enasidenib).
+We will specifically focus on recent data examining what is known about the potential risks for IFD with SMKIs used in AML treatment that define the need for prophylaxis, what are the advantages and disadvantages of using non-triazole based prophylaxis, what is known about the safety of empiric dose adjustments for SMKIs, and what the are the risks giving triazole with full-dose SMKI therapy.
+
+## Should triazole prophylaxis be stopped?
+
+\
+Should we consider non-triazole based primary prophylaxis?
+
+\

### 2022-12-09 Users/russelllewis/Desktop/AMLtargetfungal/AMLtargetfungal.tex
revision

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Short Paper},
  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Short Paper}
\author[1]{Alice Anonymous%
\corref{cor1}%
\fnref{fn1}}
 \ead{alice@example.com} 
\author[2]{Bob Security%
%
\fnref{fn2}}
 \ead{bob@example.com} 
\author[2]{Cat Memes%
%
\fnref{fn3}}
 \ead{cat@example.com} 
\author[]{Derek Zoolander%
%
}
 \ead{derek@example.com}

\affiliation[1]{organization={Some Institute of Technology, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}
\affiliation[2]{organization={Another University, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
it should be a really long footnote. But this footnote is not yet
sufficiently long enough to make two lines of footnote text.}
\fntext[fn3]{Yet another author footnote.}

\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
tempus elit.
\end{abstract}

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, breakable]}{\end{tcolorbox}}\fi

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{verbatim}
natbiboptions: longnamesfirst,angle,semicolon
\end{verbatim}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{cite-method} is set to \texttt{citeproc} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. By default, this template will provide an
appropriate style, but alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\hypertarget{figures-and-tables}{%
\section{Figures and tables}\label{figures-and-tables}}

Figure~\ref{fig-meaningless} is generated using an R chunk.

\begin{figure}

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{AMLtargetfungal_files/figure-pdf/fig-meaningless-1.pdf}

}

\caption{\label{fig-meaningless}A meaningless scatterplot}

\end{figure}

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in
Table~\ref{tbl-simple} example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl-simple}{}
\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tbl-simple}Caption centered above table}\tabularnewline
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endfirsthead
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endhead
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\bottomrule()
\end{longtable}

\renewcommand\refname{References}
  \bibliography{bibliography.bib}

\end{document}

### 2022-12-15 Manuscript.qmd
revision

@@
 title: "When Precision Therapy Creates Inprecise Choices"
-subtitle: "Antifungal prophyalxis in the era or targeted therapy for acute myelogenoys leukemia"
+subtitle: "Antifungal prophyalxis in the era or targeted therapy for acute myelogeneous leukemia"
 format: html
@@
 
-##
-
 ## Keywords
@@
 ## Competing interests
-
-##
 
@@
 The standard remission-induction chemotherapy for AML in use for over 40 years combines cytarabine and an anthracycline that results in severe and prolonged neutropenia, which places patients at high risk for developing life-threatening invasive fungal diseases (IFDs) [@taplitz_etal18] Beyond the direct mortality of these infections, IFDs can jeopardize the timing and intensity of subsequent chemotherapy treatment cycles [@girmenia2014a;@even2011] or stem cell transplantation [@cordonnier_etal95;@offner_etal98]increasing the patient's risk for leukemia relapse.
-As a result, antifungal prophylaxis, most commonly with posaconazole, has become a standard of care in many centres to reduce the risk of fungal fungal infection during remission-induction chemotherapy [@maertens_etal18; @cornely2007J]
+As a result, antifungal prophylaxis, typically posaconazole, has become a standard of care in many centres to reduce the risk of fungal fungal infection during remission-induction chemotherapy [@maertens_etal18; @cornely2007J]
 
 Progress in the knowledge of the biology and therapy of acute myeloid leukemia (AML) has evolved at a rapid pace over the last two decades.
-High resolution cytogenetics and next-generation sequencing have better defined the molecular drivers or lekemogenesis and disease progression sparking an explosion in novel "targeted thearpies" [@kantarjian2021].
+High resolution cytogenetics and next-generation sequencing have better defined the molecular drivers or lekemogenesis and malignancy progression sparking an explosion in novel "targeted thearpies" [@kantarjian2021].
 Most of these new therapies are represented by small molecule kinase inhibitors (SMKIs) that target aberrant signalling pathways that arise form somatic mutations in leukemic cells[@kantarjian_etal21].
-Targeted therapies are now being incorporated in virtually every treatment phase of AML, and increasingly are used in place of more toxic standard chemotherapy regimens in older adults who in the past were only candidates for pallative care or hospise care [@kantarjian_etal22].
+Targeted therapies are now being incorporated into every treatment phase of AML, and increasingly are used in place of more toxic standard chemotherapy regimens in older adults who in the past were only candidates for pallative care or hospise care [@kantarjian_etal22].
 
-Despite the promise of these new therapies, their clinical use in patients with AML is often complicated by drug interactions affecting their metabolic clearance through the CYP3A4/5 pathway [@bruggemann2022] Co-administration of SMKIs with mould-active triazoles such as posaconazole, can result in excessive drug exposures and serious toxicities without dosage adjustment of the SMKIs or discontinuation of the triazole.
-Therefore, clinicians are often faced with the prospect of (i) potentially stopping triazole prophylaxis to avoid interactions with the SMKI; (ii) switching to an alternative antifungal prophylaxis without CYP3A4/5 interactions; (iii) empirically reducing the dose of the SMKI to account for the effect of triazole CYP3A4/5 inhibition; and (iv) continuing both the SMKI and triazole atful dose and monitoring the patient carefully for toxicity.
-Each of these choices are associated with potential risks to patient and must be weighed carefully depending on the treatment setting and resources available for diagnostic testing and therapeutic drug monitoring.
+Despite the promise of these new therapies, their clinical use in patients with AML is often complicated by drug interactions affecting their metabolic clearance through the CYP3A4/5 pathway [@bruggemann2022].
+Co-administration of SMKIs with mould-active triazoles such as posaconazole, may result in excessive drug exposures and serious toxicities without dosage adjustment of the SMKIs or discontinuation of the triazole.
+Therefore, clinicians are often faced with the prospect of (1) potentially stopping triazole prophylaxis to avoid interactions with the SMKI; (2) switching to an alternative antifungal prophylaxis without CYP3A4/5 interactions; (3) empirically reducing the dose of the SMKI to account for the effect of triazole CYP3A4/5 inhibition but potentially increasing the risk of AML treatment failure; and (4) continuing both the SMKI and triazole at full dose and monitoring the patient carefully for toxicity.
+Each of these choices are associated with risks to patient and must be weighed carefully depending on the leukemia prognosis, treatment phase, and resources available for diagnostic testing and therapeutic drug monitoring.
 
@@
 
-\
-Should we consider non-triazole based primary prophylaxis?
+AML patients are among the highest risk groups for developing IFDs, with a reported incidence approaching 10 to 25% in recent surveys [].
+Historically, the main considered to drive  risk for IFD were related to (1) host fitness for standard chemotherapy (ie, fit, unfit, or frail); (2) leukemia resistance (high vs low probability of achieving complete remission [CR]); (3) anticipated treatment-related toxicity such as neutropenia, mucositis, and steroid-induced immunosuppression; and (4) patient exposure to opportunistic fungi.
+[Nucci and Anaissie 2014].
+## Should we consider non-triazole based primary prophylaxis?
 
-\
+## Should we empirically reduce the dose of SMKIs or continue at full-dose?
+
+### Venetoclax
+
+### FLT3 inhibitors
+
+### IDH inhibitors
+
+## Will there be a role for therapeutic drug monitoring?
+
+## Conclusions

### 2022-12-15 Manuscript.qmd
revision

--- 2022-12-06 Manuscript.qmd
@@
 ---
-title: "Managing Fungal Infections in the Era of Targeted Therapy for Acute Myelogenous Leukemia"
+title: "When Precision Therapy Creates Inprecise Choices"
+subtitle: "Antifungal prophyalxis in the era or targeted therapy for acute myelogeneous leukemia"
 format: html
@@
 
-^1^Associate Professor of Medicine, Department of Molecular Medicine, University of Padua, Padua, Italy:ORCID ID:
+^1^Associate Professor of Medicine, Department of Molecular Medicine, University of Padua, Padua, Italy:ORCID ID 000-0002-2002-4339
 
-^2^Director of Hematopoietic Stem Cell Transplantation and Cellular Therapy,   Hematology Unit, Ca' Foncello Hospital,  AULSS 2- Marca Trevigiana, Treviso, Italy:ORCID ID:
+^2^Director of Hematopoietic Stem Cell Transplantation and Cellular Therapy,   Hematology Unit, Ca' Foncello Hospital,  AULSS 2- Marca Trevigana, Treviso, Italy:ORCID ID:000-0003-1569-3447
 
-##
+# Abstract
 
-Keywords
+(150-250)
 
-## Competing interests
+\* corresponding author: russ.e.lewis\@gmail.com
 
-##
+# Keywords:
 
-## Abstract
+# Competing interests:
 
-15-250 words
+Authors are required to disclose financial or non-financial interests that are directly or indirectly related to the work submitted for publication.
+Please refer to "Competing Interests and Funding" below for more information on how to complete this section.
 
-## Introduction
+# Introduction
 
-Progress in the understanding of the biology and therapy of acute myeloid leukemia (AML) is evolving at a rapid pace.
-Recent advances in cytogenetics and next-generation sequencing have revealed that AML is a spectrum of clinical-cytogenetic-molecular entities with diverse pathophysiologies requiring different therapies associated with different outcomes [@kantarjian2008].
-This knowledge has fuelled an explosion in the development of novel therapeutics that target abnormal signalling pathways arising from somatic mutations in AML[@newell_cook21].
-Targeted therapies are now increasingly used in combination with, or in place of, traditional cytotoxic chemotherapy [@kantarjian2016].
-Since 2017, nine agents have been approved for various indications in AML [@kantarjian_etal21].
-Several of these agents have been shown to improve survival vs.conventional conventional chemotherapy in selected AML populations, especially among older patients who as little as two decades ago were only offered supportive care, palliation or hospice [@kantarjian_etal22].
+Acute myeloid leukemia (AML) is a hematologic malignancy characterized by the proliferation of myeloid blasts or progranulocytes that fail to undergo normal differentiation [@newell_cook21].
+It is the most common acute leukemia is older adults and historically associated with 5-year survival rates less than 10-15% in patients over 60 years of age [@kantarjian_etal21; @kantarjian_etal21b].
+Traditional remission-induction chemotherapy (RIC) approaches for AML used for over 40 years such as 7 days of cytarabine + 3 days of daunarubin (7+3 regimen) cause severe and prolonged neutropenia, which places patients at high risk for invasive fungal diseases (IFDs) [@taplitz_etal18].
+Beyond their direct mortality, fungal infections can jeopardize the timing and intensity of subsequent chemotherapy treatment cycles [@girmenia2014a; @even2011] or stem cell transplantation [@cordonnier_etal95]increasing the patient's risk for leukemia relapse.
+As a result, primary antifungal prophylaxis, first with fluconazole, and now more commonly with a mold-active triazole posaconazole, has become a standard of care in many centres [@maertens_etal18; @cornely2007J; @halpern2015].
 
-Classical induction chemotherapy regimens for AML with combinations of cytarabine and anthracyclines result in prolonged neutropenia that placed the patient at high risk for for developing invasive mold diseases such as aspergillosis [@pagano2016].
-Although improvements in diagnostics and newer antifungal therapies have improved outcomes, average mortality rates 6 weeks after diagnosis still approach 20% [@thompson_young21].
-For those patients who survive the infection, consolidation chemotherapy[@girmenia2014a, @offner1998; @even2011] or progression to hematopoetic stem cell transplantation[@ford_etal21] is often delayed, or eligibility for clinical trials of novel targeted agents may be impacted increasing the risk for relapse and decreased disease-free survival.
-Therefore, prevention or preemeptive control of mold infections is integral for improving the probability of durable remission of the underlying malignancy.
+Progress in the understanding of the biology and therapy of AML has evolved at a rapid pace over the last two decades.
+Advances in cytogenetic analysis and next-generation sequencing have better defined the molecular drivers of leukemogenesis and disease prognosis sparking an explosion in the development of "targeted therapies" [@kantarjian_etal21b].
+Since 2017, nine new targeted therapies have been approved by the U.S.
+Food and Drug Administration of the treatment of AML with many additional agents in clinical trials.
+These therapies are now being incorporated in virtually every treatment phase of AML, and are increasingly are used in place of more toxic standard chemotherapy regimens in older adults who in the past were only candidates for palliative care or hospice care [@kantarjian_etal21b; @kantarjian_etal22].
 
-Triazole antifungals
+Most of the recently approved targeted therapies are small molecule kinase inhibitors (SMKIs) that are metabolized through the cytochrome P450 3A4/5 oxidative enzymes in the liver [@bruggemann_etal22].
+As such, their clearance in altered by varying degree by triazole antifungals potentially resulting in higher drug exposures to the targeted chemotherapy agent and potentially serious toxicities.
+This creates a dilemma for clinicians of whether to continue to use posaconazole prophylaxis, which has a proven survival benefit in AML patients with prolonged neutropenia, but would potentially put the patient at greater risk for treatment-limiting toxicities that may increase the risk of leukemia relapse.
 
-\
+Specifically, four scenarios are often considered: (i) stopping triazole prophylaxis to avoid interactions with the SMKI; (ii) switching to an alternative antifungal prophylaxis without CYP3A4/5 interactions; (iii) empirically reducing the dose of the SMKI to account for the effect of triazole CYP3A4/5 inhibition; and (iv) continuing both the SMKI and triazole antifungal dose and monitoring the patient carefully for toxicity.
+Each of these choices create risks to patient and must be considered individually depending on the treatment scenario and resources for patient monitoring, fungal diagnostic testing and therapeutic drug monitoring.
 
-**How do targeted therapies alter the risk of invasive mold disease?**
+In this review, we address these four questions for the three most common class of prescribed SMKIs-the anti-apoptotic B/cell lymphoma-2 (Bcl-2) protein inhibitors venetoclax, fms like tyrosine kinase 3 (FLT-3) inhibitors (midostaurin, gilteritinib, quizartinib) and isocitrate dehydrogenase 1 and 2 (IDH1/2) inhibitors (ivosidenib, enasidenib).
+We will specifically focus on recent data examining what is known about the potential risks for IFD with SMKIs used in AML treatment that define the need for prophylaxis, what are the advantages and disadvantages of using non-triazole based prophylaxis, what is known about the safety of empiric dose adjustments for SMKIs, and what the are the risks giving triazole with full-dose SMKI therapy.
 
-\
+# Can primary antifungal prophylaxis during remission-induction chemotherapy with triazoles be stopped?
 
-**What are the risk with triazole antifungals?**
+The use of antifungal prophylaxis is typically justified if the infection is (1) Serious enough such that even when diagnosed early or treated preemptively the infection incurs significant morbidity and mortality; (2) considered common enough to justify universal prophylaxis of the at risk population (i.e.
+\> 10% incidence), (3) the infection is difficult to diagnose.
+The first criteria is generally accepted to be true for IFDs in AML patients.
+The second criteria of how common the infection is , will vary from center to center and individual patient characteristics.
+Although recent surveys have suggested the incidence of IFDs in patients undergoing treatment for AML typically range between 10 to 25%, there is significant variation variation from one center to the next [@pagano_etal16] Nucci and Anaissie [@nucci_anaissie14] summarized the key risk factors for developing IFD in patients undergoing treatment for AML into 4 categories:
 
-*Venetoclax*
+-   Host fitness for standard chemotherapy (i.e., fit, unfit, or frail);
+-   Leukemia resistance (high versus low probability of achieving complete remission \[CR\]) and current malignancy status
+-   Anticipated treatment-related toxicity such as neutropenia, mucositis, and steroid-induced immunosuppression
+-   Patient exposure to opportunistic fungi.
 
-\
+While these categories are still relevant, use of SMKIs and hypomethylating agents instead of intensive cytotoxic chemotherapy, especially in older patients, may alter risk for invasive fungal disease [@aldoss_etal19].
+Therefore, a central question is whether the use of targeted therapies is whether their use augments or reduces the risk of IFD in patients undergoing treatment for AML.
 
-\
+This question was the subject of recent reviews [@reinwald2018], and an expert guideline written by experts on behalf of the European Hematology Association (EHA) in cooperation with the Cochrane Hematology Group [@stemler_etal22].
+For the resulting guidelines, studies including 19 relevant novel targeted agents currently approved or in later stages of clinical trials were reviewed, summarized and depending on available evidence, prepared as consensus-based recommendations despite the lack of high-quality studies assessing the use of antifungal agents in this setting [@stemler_etal22; @stemler_cornely22].
+A summary of the recommendations for key approved agents is provided in [@tbl-drugs], the continued use of posaconazole prophylaxis was still recommended if patients are receiving targeted therapies as part of standard RIC.
+However, in consolidation chemotherapy, the risk of IFD is generally lower especially for invasive aspergillosis unless the patient has persistent neutropenia or prior fungal infections [@pagano_etal16], therefore continued use of posaconazole prophylaxis in patients received targeted therapies as maintenance or consolidation chemotherapy is conditional on the patient-specific risks.
+In this respect, we have found individualized risk stratification tools, such as institutionally-validated risk scores for aspergillosis [@stanzani_etal19;@stanzani_lewis18]to be helpful for decisions of whether continued prophylaxis is necessary.
+
+The third key criteria supporting the use of prophylaxis is diagnostic difficulty.
+The availability of improved diagnostic tools (serum galactomannan, PCR) and high-resolution CT scanning has improved the early diagnosis of these infections allowing for possible or a preemeptive treatment approaches- i.e.
+initiation of antifungal therapy after detection of early fungal biomarkers and suggestive chest CT findings.
+Preemptive management approaches for IFD have been shown to be as effective as empirical treatment in high-risk patients with persistent fever [@morrissey2013].
+An EORTC-lead randomized trial demonstrated that preemptive antifungal strategy was safe for high-risk neutropenic patients given fluconazole as prophylaxis, halving the number of patients receiving mould-active antifungals without excess mortality or IFDs .
+However, primary antifungal prophylaxis with posaconazole has not been directly compared with empiric or preemptive therapy in a randomized clinical trial during RIC for AML.
+
+In allogeneic HSCT recipients, a preemptive-like approach (fluconazole prophylaxis plus galactomannan monitoring) was proven to be as safe and effective as voriconazole prophylaxis both in terms of 6-month fungal-free survival (FFS) and relapse-free and overall survival {Wingard et al., 2010, #305904}.
+However, in patients transplanted for AML, patients who received voriconazole prophylaxis versus the preemptive approach experienced significantly fewer cases of IFD (8.5% vs.
+21%, P=0.04) and had improved FFS (78% vs.
+61%, P=0.04) and a trend towards improved overall survival (81% vs.
+72%, P=0.32) {Wingard et al., 2010, #305904}.
+Therefore, the equivalence of preemptive versus prophylactic approach for the highest groups remains unproven {Coussement et al., 2021, #228156}.
+However, the safety of a preemptive approach in lieu of continued prophylaxis seems feasible in patients on SMKIs during consolidation phase, provided there is rapid availability to CT scanning and mycological testing, including when patients are in the outpatient setting where the bulk of these treatments are now being administered.
+
+Collectively, the evidence does not seem to currently support abandoning primary antifungal prophylaxis in AML patients receiving SMKIs during RIC when the risk of IFD is highest.
+However, primary antifungal prophylaxis mold-active triazoles may be unnecessary for patients receiving lower- intensity therapy with a hypomethylating agent (decitabine or azacitidine) or low-dose cytarabine alone combined with drugs such as venetoclax unless extenuating risk factors are present, such as prolonged neutropenia {Nucci and Anaissie, 2014, #67476}.
+In these patients a preemptive or empiric management approach may be appropriate in lieu of continued prophylaxis to reduce the risk of toxicity and drug interactions with the SMKIs.
+
+# Should the patient be switched to alternative antifungal prophylaxis without CYP3A4/5 interactions?
+
+Non-triazole based agents, namely echinocandins or liposomal amphotericin B, are often considered as alternatives to triazoles in patients who require SMKIs or are enrolled in clinical trials with new targeted therapies that preclude use triazoles because of QT-prolongation risk {Brüggemann et al., 2022, #246315}.
+Currently, only micafungin is approved for prophylaxis of Candida infection in patients undergoing allogeneic hematopoietic stem cell transplantation or patients who are expected to have neutropenia (absolute neutrophil count \< 500 cells / µl) for 10 or more days.
+Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA {Herbrecht et al., 2010, #83826; Ullmann et al., 2012, #93212; Viscoli et al., 2009, #67612}.
+A recent open-label randomized trial comparing caspofungin to fluconazole prophylaxis in children and adolescents undergoing treatment for AML found significantly lower cumulative incidence of proven or probable aspergillosis in patient who received caspofungin versus fluconazole (0.5% vs.
+3%, P=0.04) {Fisher et al., 2019, #304611}, although the rates of IA in the fluconazole arm were lower than reported in previous adult studies that compared posaconazole suspension to fluconazole/itraconazole (1% vs.
+7%, P=0.04){Cornely et al., 2007, #18388}.
+Some {Gomes et al., 2014, #19244} but not all{Epstein et al., 2018, #24798;El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.
+
+Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast {Stanzani et al., 2019, #287617;Gomes et al., 2013, #95041; El Zein et al., 2020, #229138} and intrinsically-resistant mold such as Fusarium spp.
+and Mucorales compared to mould-active triazoles {Gomes et al., 2013, #95041}.
+In centers or regions where these infections are more common, careful consideration should be given to early diagnosis of these breakthrough infections given their propensity for fulminant infections and rapid dissemination.
+
+Intravenous liposomal amphotericin B (L-AMB) is occasionally used off-label as a prophylaxis agent, although the optimal dosing approach and efficacy is not well established.
+This approach was often considered adult patients with acute lymphoblastic leukemic (ALL), who frequently receive chemotherapy regimens containing vinca alkaloids, which are metabolized through CYP3A4 {Stafylidis et al., 2022, #235425}.
+Cornely et al.
+performed a double-blind multicenter Phase 3 study comparing twice-weekly prophylactic liposomal amphotericin B (L-AMB) at 5 mg/kg intravenously or placebo twice during remission-induction treatment {Cornely et al., 2017, #34343}.
+Rates of proven and probable IFD were similar between L-AMB and placebo (7.9% vs.
+11.7) with similar mortality rates.
+Hypokalaemia (35.0% vs.
+17.8%) and increased creatinine (\> 1.5x baseline, 3.0% vs.
+0%) were significantly more frequent in patients who received L-AMB prophylaxis.
+It is unclear if the limited efficacy was a reflection of the infrequent dosing regimen- therefore, if L-AMB is considered it may be more judicious to administer a daily 3 mg/kg dose for a define period (i.e.
+\< 21 days) if in unique cases L-AMB prophylaxis is used in patients who cannot tolerate triazoles or echinocandins.
+
+Both echinocandins and liposomal amphotericin B must be administered intravenously, making them more problematic to use in the outpatient setting in patients taking SMKIs as part of a consolidation- maintenance regimen.
+An oral echinocandin-like triterpenoid recently approved for the treatment of vuvlvovaginal candidiasis, ibrexafungerp, is currently under investigations
+
+If a triazole must be given, is isavuconazole the preferred?
+
+What will be the potential role of new antifungals?
+
+Table
+
+Should the dose of the SMKI by empirically reduced to account for the effect of triazole CYP3A4/5 inhibition?
+
+Venetoclax
 
@@
 
-**What are the risks with echinocandins?**
+IDH1/2 inhibitors
 
-\
+What is the role of therapeutic drug monitoring?
 
-**What are the risk with liposomal amphotericin B?**
+## Conclusions
 
-\
++-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Targeted therapy                                      | Molecular target                                                                        | Mechanisms of immunosuppression risk                                                  | Impact of invasive fungal disease                                                                                                                                         | Triazole prophylaxis recommendation                                                                                                                                                                                                                   |
++=======================================================+=========================================================================================+=======================================================================================+===========================================================================================================================================================================+=======================================================================================================================================================================================================================================================+
+| **Hypomethylating agents** (azacitabione, decitabine) | Inhibition of DNA methyltransferase that hypermethylase tumor suppressor gene promoters | Mild neutropenia and gastrointestinal toxicity                                        | Reported incidence in clinical studies 2.6-14.4%;                                                                                                                         | Conditional depending if neutropenia present at onset of use, or when used in combination with venetoclax.
+No dosage adjustment required when given with triazole.
+|
+|                                                       |                                                                                         |                                                                                       |                                                                                                                                                                           |                                                                                                                                                                                                                                                       |
+|                                                       |                                                                                         |                                                                                       | Low risk if used alone, but risk is higher when used in combination with venetoclax or in patients with prior neutropenia.
+|                                                                                                                                                                                                                                                       |
++-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| **Gemtuzumab-ozogamacin**                             | Humanized CD33-directed monoclonal antibody drug conjugate                              | Neutropenia, typically in combination with cytotoxic remission-induction chemotherapy | Limited evidence of increased risk for IFD above conventional remission-induction chemotherapy                                                                            | Triazole prophylaxis recommended when drug is used in combination for remission-induction chemotherapy.
+No dosage adjustment required when given with triazole.
+|
++-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| **BCL-2 inhibitor**                                   | Selective inhibitor of anti-apoptosis protein BCL2                                      | Neutropenia                                                                           | Limited evidence but overall risk is low, except in patients with prior allogeneic stem cell transplant, prolonged neutropenia, or when used for resistant/refractory AML | Conditional, but should be considered for patients with prolonged neutropenia.
+Dosage adjustment required when given with triazole                                                                                                                    |
+|                                                       |                                                                                         |                                                                                       |                                                                                                                                                                           |                                                                                                                                                                                                                                                       |
+| (venetoclax)                                          |                                                                                         |                                                                                       |                                                                                                                                                                           |                                                                                                                                                                                                                                                       |
++-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| **FLT3 inhibitors** (midostaurin, gilteritinib)       | Inhibition of fms like tyrosine kinase 3                                                | Neutropenia                                                                           | Limited evidence, no studies to date suggesting increased risk                                                                                                            | Triazole prophylaxis recommended when given as part of remission-induction chemotherapy.
+Individualized decisions when given as part of maintenance chemotherapy.
+Patients must be monitored closely for toxicities due to expected drug interactions |
++-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| I**DH1/2 inhibitors**                                 | Isocitrate dihydrogenase i/ 2 enzyme inhibitors                                         | Toxicity                                                                              | Limited evidence, no studies to date suggesting increased risk                                                                                                            | Conditional, but should be considered for patients with prolonged neutropenia.
+|
+|                                                       |                                                                                         |                                                                                       |                                                                                                                                                                           |                                                                                                                                                                                                                                                       |
+| (ivosidinib, enasidenib)                              |                                                                                         |                                                                                       |                                                                                                                                                                           |                                                                                                                                                                                                                                                       |
++-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
 
-**What is the promise of future antifungals?**
-
-\
-
-**What is the role of therapeutic drug monitoring?**
+: EHA Guidelines on Antifungal Prophylaxis in AML in Adult Patients Treatment with Novel Targeted Therapies.n {#tbl-drugs}

### 2022-12-15 Manuscript.qmd
revision

@@
 However, in consolidation chemotherapy, the risk of IFD is generally lower especially for invasive aspergillosis unless the patient has persistent neutropenia or prior fungal infections [@pagano_etal16], therefore continued use of posaconazole prophylaxis in patients received targeted therapies as maintenance or consolidation chemotherapy is conditional on the patient-specific risks.
-In this respect, we have found individualized risk stratification tools, such as institutionally-validated risk scores for aspergillosis [@stanzani_etal19;@stanzani_lewis18]to be helpful for decisions of whether continued prophylaxis is necessary.
+In this respect, we have found individualized risk stratification tools, such as institutionally-validated risk scores for aspergillosis [@stanzani_etal19; @stanzani_lewis18]to be helpful for decisions of whether continued prophylaxis is necessary.
 
@@
 Preemptive management approaches for IFD have been shown to be as effective as empirical treatment in high-risk patients with persistent fever [@morrissey2013].
-An EORTC-lead randomized trial demonstrated that preemptive antifungal strategy was safe for high-risk neutropenic patients given fluconazole as prophylaxis, halving the number of patients receiving mould-active antifungals without excess mortality or IFDs .
+An EORTC-lead randomized trial demonstrated that preemptive antifungal strategy was safe for high-risk neutropenic patients given fluconazole as prophylaxis, halving the number of patients receiving mould-active antifungals without excess mortality or IFDs [@Maertens2022].
 However, primary antifungal prophylaxis with posaconazole has not been directly compared with empiric or preemptive therapy in a randomized clinical trial during RIC for AML.
 
-In allogeneic HSCT recipients, a preemptive-like approach (fluconazole prophylaxis plus galactomannan monitoring) was proven to be as safe and effective as voriconazole prophylaxis both in terms of 6-month fungal-free survival (FFS) and relapse-free and overall survival {Wingard et al., 2010, #305904}.
+In allogeneic HSCT recipients, a preemptive-like approach (fluconazole prophylaxis plus galactomannan monitoring) was proven to be as safe and effective as voriconazole prophylaxis both in terms of 6-month fungal-free survival (FFS) and relapse-free and overall survival [@Wingard2010a].
 However, in patients transplanted for AML, patients who received voriconazole prophylaxis versus the preemptive approach experienced significantly fewer cases of IFD (8.5% vs.
@@
 61%, P=0.04) and a trend towards improved overall survival (81% vs.
-72%, P=0.32) {Wingard et al., 2010, #305904}.
-Therefore, the equivalence of preemptive versus prophylactic approach for the highest groups remains unproven {Coussement et al., 2021, #228156}.
+72%, P=0.32).
+Therefore, the equivalence of preemptive versus prophylactic approach for the highest groups remains unproven [@Coussement2021].
 However, the safety of a preemptive approach in lieu of continued prophylaxis seems feasible in patients on SMKIs during consolidation phase, provided there is rapid availability to CT scanning and mycological testing, including when patients are in the outpatient setting where the bulk of these treatments are now being administered.
@@
 Collectively, the evidence does not seem to currently support abandoning primary antifungal prophylaxis in AML patients receiving SMKIs during RIC when the risk of IFD is highest.
-However, primary antifungal prophylaxis mold-active triazoles may be unnecessary for patients receiving lower- intensity therapy with a hypomethylating agent (decitabine or azacitidine) or low-dose cytarabine alone combined with drugs such as venetoclax unless extenuating risk factors are present, such as prolonged neutropenia {Nucci and Anaissie, 2014, #67476}.
-In these patients a preemptive or empiric management approach may be appropriate in lieu of continued prophylaxis to reduce the risk of toxicity and drug interactions with the SMKIs.
+However, primary antifungal prophylaxis mold-active triazoles may be unnecessary for patients receiving lower- intensity therapy with a hypomethylating agent (decitabine or azacitidine) or low-dose cytarabine alone combined with drugs such as venetoclax unless extenuating risk factors are present, such as prolonged neutropenia [@nucci_anaissie14] In these patients a preemptive or empiric management approach may be appropriate in lieu of continued prophylaxis to reduce the risk of toxicity and drug interactions with the SMKIs.
 
@@
 
-Non-triazole based agents, namely echinocandins or liposomal amphotericin B, are often considered as alternatives to triazoles in patients who require SMKIs or are enrolled in clinical trials with new targeted therapies that preclude use triazoles because of QT-prolongation risk {Brüggemann et al., 2022, #246315}.
+Non-triazole based agents, namely echinocandins or liposomal amphotericin B, are often considered as alternatives to triazoles in patients who require SMKIs or are enrolled in clinical trials with new targeted therapies that preclude use triazoles because of QT-prolongation risk [@bruggemann_etal22].
 Currently, only micafungin is approved for prophylaxis of Candida infection in patients undergoing allogeneic hematopoietic stem cell transplantation or patients who are expected to have neutropenia (absolute neutrophil count \< 500 cells / µl) for 10 or more days.
-Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA {Herbrecht et al., 2010, #83826; Ullmann et al., 2012, #93212; Viscoli et al., 2009, #67612}.
+Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA [@ullmann2012a; @viscoli2009; @herbrecht2010a].
 A recent open-label randomized trial comparing caspofungin to fluconazole prophylaxis in children and adolescents undergoing treatment for AML found significantly lower cumulative incidence of proven or probable aspergillosis in patient who received caspofungin versus fluconazole (0.5% vs.
-3%, P=0.04) {Fisher et al., 2019, #304611}, although the rates of IA in the fluconazole arm were lower than reported in previous adult studies that compared posaconazole suspension to fluconazole/itraconazole (1% vs.
-7%, P=0.04){Cornely et al., 2007, #18388}.
-Some {Gomes et al., 2014, #19244} but not all{Epstein et al., 2018, #24798;El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+3%, P=0.04) [@fisher_etal19a], although the rates of IA in the fluconazole arm were lower than reported in previous adult studies that compared posaconazole suspension to fluconazole/itraconazole (1% vs.
+7%, P=0.04) [@cornely2007J].
+Some [@gomes2014] but not all [@Epstein2018a]{Epstein et al., 2018, #24798;El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
 Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.

### 2022-12-15 Manuscript.qmd
Update Manuscript.qmd
revision

@@
 7%, P=0.04) [@cornely2007J].
-Some [@gomes2014] but not all [@Epstein2018a]{Epstein et al., 2018, #24798;El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+Some [@gomes2014] but not all [@Epstein2018a];El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
 Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.
 
-Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast {Stanzani et al., 2019, #287617;Gomes et al., 2013, #95041; El Zein et al., 2020, #229138} and intrinsically-resistant mold such as Fusarium spp.
+Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast {Stanzani et al., 2019, #287617;Gomes et al., 2013, #95041; El Zein et al., 2020, #229138} and intrinsically-resistant mold such as *Fusarium* spp.
 and Mucorales compared to mould-active triazoles {Gomes et al., 2013, #95041}.

### 2022-12-16 Manuscript.qmd
revision

@@
 initiation of antifungal therapy after detection of early fungal biomarkers and suggestive chest CT findings.
-Preemptive management approaches for IFD have been shown to be as effective as empirical treatment in high-risk patients with persistent fever [@morrissey2013].
-An EORTC-lead randomized trial demonstrated that preemptive antifungal strategy was safe for high-risk neutropenic patients given fluconazole as prophylaxis, halving the number of patients receiving mould-active antifungals without excess mortality or IFDs [@Maertens2022].
+Preemptive management approaches for IFD have been shown to be as effective as empirical treatment in high-risk patients with persistent fever [@morrissey_etal13].
+An EORTC-lead randomized trial demonstrated that preemptive antifungal strategy was safe for high-risk neutropenic patients given fluconazole as prophylaxis, halving the number of patients receiving mould-active antifungals without excess mortality or IFDs [@maertens_etal22].
 However, primary antifungal prophylaxis with posaconazole has not been directly compared with empiric or preemptive therapy in a randomized clinical trial during RIC for AML.
@@
 Currently, only micafungin is approved for prophylaxis of Candida infection in patients undergoing allogeneic hematopoietic stem cell transplantation or patients who are expected to have neutropenia (absolute neutrophil count \< 500 cells / µl) for 10 or more days.
-Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA [@ullmann2012a; @viscoli2009; @herbrecht2010a].
+Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA [@Ullmann2018; @Viscoli2009; @Herbrecht2010].
 A recent open-label randomized trial comparing caspofungin to fluconazole prophylaxis in children and adolescents undergoing treatment for AML found significantly lower cumulative incidence of proven or probable aspergillosis in patient who received caspofungin versus fluconazole (0.5% vs.
-3%, P=0.04) [@fisher_etal19a], although the rates of IA in the fluconazole arm were lower than reported in previous adult studies that compared posaconazole suspension to fluconazole/itraconazole (1% vs.
+3%, P=0.04) [@Fisher2019], although the rates of IA in the fluconazole arm were lower than reported in previous adult studies that compared posaconazole suspension to fluconazole/itraconazole (1% vs.
 7%, P=0.04) [@cornely2007J].
-Some [@gomes2014] but not all [@Epstein2018a];El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+Some [@gomes2014] but not all [@Epstein2018;@El-Cheikh2013]single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
 Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.
 
-Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast {Stanzani et al., 2019, #287617;Gomes et al., 2013, #95041; El Zein et al., 2020, #229138} and intrinsically-resistant mold such as *Fusarium* spp.
-and Mucorales compared to mould-active triazoles {Gomes et al., 2013, #95041}.
+Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast [@stanzani_etal19;@Gomes2014;@El2020]and intrinsically-resistant mold such as Fusarium spp.
+and Mucorales compared to mould-active triazoles [@Gomes2014].
 In centers or regions where these infections are more common, careful consideration should be given to early diagnosis of these breakthrough infections given their propensity for fulminant infections and rapid dissemination.
@@
 Intravenous liposomal amphotericin B (L-AMB) is occasionally used off-label as a prophylaxis agent, although the optimal dosing approach and efficacy is not well established.
-This approach was often considered adult patients with acute lymphoblastic leukemic (ALL), who frequently receive chemotherapy regimens containing vinca alkaloids, which are metabolized through CYP3A4 {Stafylidis et al., 2022, #235425}.
+This approach was often considered adult patients with acute lymphoblastic leukemic (ALL), who frequently receive chemotherapy regimens containing vinca alkaloids, which are metabolised through CYP3A4 [@Stafylidis2022].
 Cornely et al.
-performed a double-blind multicenter Phase 3 study comparing twice-weekly prophylactic liposomal amphotericin B (L-AMB) at 5 mg/kg intravenously or placebo twice during remission-induction treatment {Cornely et al., 2017, #34343}.
+performed a double-blind multicenter Phase 3 study comparing twice-weekly prophylactic liposomal amphotericin B (L-AMB) at 5 mg/kg intravenously or placebo twice during remission-induction treatment [@Cornely2017].
 Rates of proven and probable IFD were similar between L-AMB and placebo (7.9% vs.
@@
 Both echinocandins and liposomal amphotericin B must be administered intravenously, making them more problematic to use in the outpatient setting in patients taking SMKIs as part of a consolidation- maintenance regimen.
-An oral echinocandin-like triterpenoid recently approved for the treatment of vuvlvovaginal candidiasis, ibrexafungerp, is currently under investigations
+An oral echinocandin-like triterpenoid recently approved for the treatment of vuvlvovaginal candidiasis, ibrexafungerp, is currently under investigation for the treatment of invasive candidiasis and treatment of invasive aspergillosis in combination with voriconazole[@johnson2021].
 
-If a triazole must be given, is isavuconazole the preferred?
+##
 
-What will be the potential role of new antifungals?
+# Should the dose of the SMKI by empirically reduced to account for the effect of triazole CYP3A4/5 inhibition?
 
-Table
+## Venetoclax
 
-Should the dose of the SMKI by empirically reduced to account for the effect of triazole CYP3A4/5 inhibition?
+## FLT3 inhibitors
 
-Venetoclax
+## IDH1/2 inhibitors
 
-FLT3 inhibitors
+## What is the role of therapeutic drug monitoring?
 
-IDH1/2 inhibitors
-
-What is the role of therapeutic drug monitoring?
+# What are the risks of continuing triazoles and SMKIs at full-dose?
 

### 2022-12-19 Manuscript.qmd
revision

@@
 It is the most common acute leukemia is older adults and historically associated with 5-year survival rates less than 10-15% in patients over 60 years of age [@kantarjian_etal21; @kantarjian_etal21b].
-Traditional remission-induction chemotherapy (RIC) approaches for AML used for over 40 years such as 7 days of cytarabine + 3 days of daunarubin (7+3 regimen) cause severe and prolonged neutropenia, which places patients at high risk for invasive fungal diseases (IFDs) [@taplitz_etal18].
-Beyond their direct mortality, fungal infections can jeopardize the timing and intensity of subsequent chemotherapy treatment cycles [@girmenia2014a; @even2011] or stem cell transplantation [@cordonnier_etal95]increasing the patient's risk for leukemia relapse.
+Traditional remission-induction chemotherapy (RIC) approaches for AML in use for over 40 years such as 7 days of cytarabine + 3 days of daunorubicin (7+3 regimen) cause severe and prolonged neutropenia, which places patients at high risk for invasive fungal diseases (IFDs) [@taplitz_etal18].
+Beyond their direct mortality risk, fungal infections can jeopardize the timing and intensity of subsequent chemotherapy treatment cycles [@girmenia2014a; @even2011] or stem cell transplantation [@cordonnier_etal95] increasing the patient's risk for leukemia relapse.
 As a result, primary antifungal prophylaxis, first with fluconazole, and now more commonly with a mold-active triazole posaconazole, has become a standard of care in many centres [@maertens_etal18; @cornely2007J; @halpern2015].
@@
 Advances in cytogenetic analysis and next-generation sequencing have better defined the molecular drivers of leukemogenesis and disease prognosis sparking an explosion in the development of "targeted therapies" [@kantarjian_etal21b].
-Since 2017, nine new targeted therapies have been approved by the U.S.
-Food and Drug Administration of the treatment of AML with many additional agents in clinical trials.
-These therapies are now being incorporated in virtually every treatment phase of AML, and are increasingly are used in place of more toxic standard chemotherapy regimens in older adults who in the past were only candidates for palliative care or hospice care [@kantarjian_etal21b; @kantarjian_etal22].
+Since 2017, nine new targeted therapies have been approved for the treatment of AML by the U.S.
+Food and Drug Administration, with many additional agents in clinical trials.
+These therapies are now being incorporated in every treatment phase of AML, and are increasingly are used in place of more toxic standard chemotherapy regimens in older adults who in the past were only candidates for palliative care or hospice care [@kantarjian_etal21b; @kantarjian_etal22].
 
-Most of the recently approved targeted therapies are small molecule kinase inhibitors (SMKIs) that are metabolized through the cytochrome P450 3A4/5 oxidative enzymes in the liver [@bruggemann_etal22].
-As such, their clearance in altered by varying degree by triazole antifungals potentially resulting in higher drug exposures to the targeted chemotherapy agent and potentially serious toxicities.
-This creates a dilemma for clinicians of whether to continue to use posaconazole prophylaxis, which has a proven survival benefit in AML patients with prolonged neutropenia, but would potentially put the patient at greater risk for treatment-limiting toxicities that may increase the risk of leukemia relapse.
+Most of the recently approved targeted therapies are small molecule kinase inhibitors (SMKIs) metabolised through the cytochrome P450 3A4/5 oxidative enzymes [@bruggemann_etal22].
+The clearance of SMKIs is inhibited to varying degrees by triazole antifungals potentially resulting in serious toxicities.
+This creates a dilemma for clinician of whether triazole prophylaxis should be continued, even if the patient is put at greater risk for treatment-limiting toxicities with the SMKI therapy.
 
-Specifically, four scenarios are often considered: (i) stopping triazole prophylaxis to avoid interactions with the SMKI; (ii) switching to an alternative antifungal prophylaxis without CYP3A4/5 interactions; (iii) empirically reducing the dose of the SMKI to account for the effect of triazole CYP3A4/5 inhibition; and (iv) continuing both the SMKI and triazole antifungal dose and monitoring the patient carefully for toxicity.
-Each of these choices create risks to patient and must be considered individually depending on the treatment scenario and resources for patient monitoring, fungal diagnostic testing and therapeutic drug monitoring.
+Specifically, four scenarios are often considered for patients who require both triazole antifungals and SMKI therapy: (i) stopping triazole prophylaxis to avoid interactions with the SMKI; (ii) switching to an alternative antifungal prophylaxis without CYP3A4/5 interactions; (iii) empirically reducing the dose of the SMKI to account for the effect of triazole CYP3A4/5 inhibition; and (iv) continuing both the SMKI and triazole antifungal dose and monitoring the patient carefully for toxicity.
+Each of these choices is associated with specific risks to patient and must be considered individually depending on the treatment scenario and resources for patient monitoring, fungal diagnostic testing and therapeutic drug monitoring.
 
 In this review, we address these four questions for the three most common class of prescribed SMKIs-the anti-apoptotic B/cell lymphoma-2 (Bcl-2) protein inhibitors venetoclax, fms like tyrosine kinase 3 (FLT-3) inhibitors (midostaurin, gilteritinib, quizartinib) and isocitrate dehydrogenase 1 and 2 (IDH1/2) inhibitors (ivosidenib, enasidenib).
-We will specifically focus on recent data examining what is known about the potential risks for IFD with SMKIs used in AML treatment that define the need for prophylaxis, what are the advantages and disadvantages of using non-triazole based prophylaxis, what is known about the safety of empiric dose adjustments for SMKIs, and what the are the risks giving triazole with full-dose SMKI therapy.
+We will specifically focus on recent data examining what is known about the potential risks for IFD with SMKIs used in AML treatment that define the need for prophylaxis, what are the advantages and disadvantages of using non-triazole based prophylaxis, and review the safety of empiric dose adjustments for SMKIs, and what the are the risks giving triazole with full-dose SMKI therapy.
 
@@
 
-The use of antifungal prophylaxis is typically justified if the infection is (1) Serious enough such that even when diagnosed early or treated preemptively the infection incurs significant morbidity and mortality; (2) considered common enough to justify universal prophylaxis of the at risk population (i.e.
-\> 10% incidence), (3) the infection is difficult to diagnose.
-The first criteria is generally accepted to be true for IFDs in AML patients.
-The second criteria of how common the infection is , will vary from center to center and individual patient characteristics.
-Although recent surveys have suggested the incidence of IFDs in patients undergoing treatment for AML typically range between 10 to 25%, there is significant variation variation from one center to the next [@pagano_etal16] Nucci and Anaissie [@nucci_anaissie14] summarized the key risk factors for developing IFD in patients undergoing treatment for AML into 4 categories:
+The use of antifungal prophylaxis is typically justified if the infection is (1) Sufficiently serious such that even when diagnosed early or treated preemptively the infection incurs significant morbidity and mortality; (2) The infection is considered common enough to justify universal prophylaxis of the at risk population (i.e.
+\> 10% incidence), (3) The infection is difficult to diagnose.
+
+The seriousness of IFD as an infectious complication in patients undergoing treatment for AML is universally accepted.
+The incidence of infection, however, will vary from center to center and individual patient characteristics.
+Although recent surveys have reported the incidence of IFDs in patients undergoing treatment for AML  between 10 to 25%, there is significant variation variation from one center to the next [@pagano_etal16] Nucci and Anaissie [@nucci_anaissie14] summarized the key risk factors for developing IFD in patients undergoing treatment for AML into 4 categories:
 
@@
 While these categories are still relevant, use of SMKIs and hypomethylating agents instead of intensive cytotoxic chemotherapy, especially in older patients, may alter risk for invasive fungal disease [@aldoss_etal19].
-Therefore, a central question is whether the use of targeted therapies is whether their use augments or reduces the risk of IFD in patients undergoing treatment for AML.
+Therefore, a key question is whether the use of targeted therapies augments or reduces the risk of IFD in patients undergoing treatment for AML.
 
-This question was the subject of recent reviews [@reinwald2018], and an expert guideline written by experts on behalf of the European Hematology Association (EHA) in cooperation with the Cochrane Hematology Group [@stemler_etal22].
-For the resulting guidelines, studies including 19 relevant novel targeted agents currently approved or in later stages of clinical trials were reviewed, summarized and depending on available evidence, prepared as consensus-based recommendations despite the lack of high-quality studies assessing the use of antifungal agents in this setting [@stemler_etal22; @stemler_cornely22].
+This risks associated with targeted therapies has been the subject of recent reviews [@reinwald2018;], and an expert guideline written by experts on behalf of the European Hematology Association (EHA) in cooperation with the Cochrane Hematology Group [@stemler_etal22].
+For the guidelines, studies including 19 relevant novel targeted agents currently approved or in later stages of clinical trials were reviewed, summarized and depending on available evidence, prepared as consensus-based recommendations despite the lack of high-quality studies assessing the use of antifungal agents in this setting [@stemler_etal22; @stemler_cornely22].
 A summary of the recommendations for key approved agents is provided in [@tbl-drugs], the continued use of posaconazole prophylaxis was still recommended if patients are receiving targeted therapies as part of standard RIC.
@@
 
-In allogeneic HSCT recipients, a preemptive-like approach (fluconazole prophylaxis plus galactomannan monitoring) was proven to be as safe and effective as voriconazole prophylaxis both in terms of 6-month fungal-free survival (FFS) and relapse-free and overall survival [@Wingard2010a].
-However, in patients transplanted for AML, patients who received voriconazole prophylaxis versus the preemptive approach experienced significantly fewer cases of IFD (8.5% vs.
-21%, P=0.04) and had improved FFS (78% vs.
+In allogeneic HSCT recipients, a preemptive strategy (fluconazole prophylaxis plus galactomannan monitoring) was proven to be as safe and effective as voriconazole prophylaxis both in terms of 6-month fungal-free survival (FFS) and relapse-free and overall survival [@Wingard2010a].
+However, voriconazole prophylaxis was associated with significantly fewer cases of IFD in patients transplanted for AML (8.5% vs.
+21%, P=0.04), with improved FFS (78% vs.
 61%, P=0.04) and a trend towards improved overall survival (81% vs.
@@
 Therefore, the equivalence of preemptive versus prophylactic approach for the highest groups remains unproven [@Coussement2021].
-However, the safety of a preemptive approach in lieu of continued prophylaxis seems feasible in patients on SMKIs during consolidation phase, provided there is rapid availability to CT scanning and mycological testing, including when patients are in the outpatient setting where the bulk of these treatments are now being administered.
+The safety of a preemptive approach in lieu of continued prophylaxis may be better supported for patients on SMKIs during consolidation phase, provided there is rapid availability to CT scanning and mycological testing, including when patients are in the outpatient setting where the bulk of these treatments are now being administered.
 
@@
 
+Non-triazole based agents, namely echinocandins or liposomal amphotericin B, are often considered as alternatives to triazoles in patients who require SMKIs or are enrolled in clinical trials with new targeted therapies that preclude use triazoles because of QT-prolongation risk [@bruggemann_etal22].
+Currently, only micafungin is approved for prophylaxis of Candida infection in patients undergoing allogeneic hematopoietic stem cell transplantation or patients who are expected to have neutropenia (absolute neutrophil count \< 500 cells / µl) for 10 or more days.
+Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA [@ullmann2012a; @viscoli2009; @herbrecht2010a].
+A recent open-label randomized trial comparing caspofungin to fluconazole prophylaxis in children and adolescents undergoing treatment for AML found significantly lower cumulative incidence of proven or probable aspergillosis in patient who received caspofungin versus fluconazole (0.5% vs.
+3%, P=0.04) [@fisher_etal19a], although the rates of IA in the fluconazole arm were lower than reported in previous adult studies that compared posaconazole suspension to fluconazole/itraconazole (1% vs.
+7%, P=0.04) [@cornely2007J].
+Some [@gomes2014] but not all [@Epstein2018a];El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.
+
+Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast {Stanzani et al., 2019, #287617;Gomes et al., 2013, #95041; El Zein et al., 2020, #229138} and intrinsically-resistant mold such as *Fusarium* spp.
+and Mucorales compared to mould-active triazoles {Gomes et al., 2013, #95041}.
+In centers or regions where these infections are more common, careful consideration should be given to early diagnosis of these breakthrough infections given their propensity for fulminant infections and rapid dissemination.
+
 Intravenous liposomal amphotericin B (L-AMB) is occasionally used off-label as a prophylaxis agent, although the optimal dosing approach and efficacy is not well established.
@@
 An oral echinocandin-like triterpenoid recently approved for the treatment of vuvlvovaginal candidiasis, ibrexafungerp, is currently under investigation for the treatment of invasive candidiasis and treatment of invasive aspergillosis in combination with voriconazole[@johnson2021].
-
-##
 
@@
 +-------------------------------------------------------+-----------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
-| I**DH1/2 inhibitors**                                 | Isocitrate dihydrogenase i/ 2 enzyme inhibitors                                         | Toxicity                                                                              | Limited evidence, no studies to date suggesting increased risk                                                                                                            | Conditional, but should be considered for patients with prolonged neutropenia.
+| **IDH1/2 inhibitors**                                 | Isocitrate dihydrogenase i/ 2 enzyme inhibitors                                         | Toxicity                                                                              | Limited evidence, no studies to date suggesting increased risk                                                                                                            | Conditional, but should be considered for patients with prolonged neutropenia.
 |

### 2022-12-19 Manuscript.qmd
revision

@@
 7%, P=0.04) [@cornely2007J].
-Some [@gomes2014] but not all [@Epstein2018;@El-Cheikh2013]single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+Some [@gomes2014] but not all [@Epstein2018; @El-Cheikh2013]single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
 Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.
 
-Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast [@stanzani_etal19;@Gomes2014;@El2020]and intrinsically-resistant mold such as Fusarium spp.
+Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast [@stanzani_etal19; @Gomes2014; @El2020]and intrinsically-resistant mold such as Fusarium spp.
 and Mucorales compared to mould-active triazoles [@Gomes2014].
@@
 Currently, only micafungin is approved for prophylaxis of Candida infection in patients undergoing allogeneic hematopoietic stem cell transplantation or patients who are expected to have neutropenia (absolute neutrophil count \< 500 cells / µl) for 10 or more days.
-Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA [@ullmann2012a; @viscoli2009; @herbrecht2010a].
+Current guidelines for the treatment of invasive aspergillosis do not recommend echinocandin monotherapy as a frontline treatment for invasive aspergillosis due to limited evidence of efficacy in patients with probable or proven IA [@Ullmann2018].
 A recent open-label randomized trial comparing caspofungin to fluconazole prophylaxis in children and adolescents undergoing treatment for AML found significantly lower cumulative incidence of proven or probable aspergillosis in patient who received caspofungin versus fluconazole (0.5% vs.
@@
 7%, P=0.04) [@cornely2007J].
-Some [@gomes2014] but not all [@Epstein2018a];El Cheikh et al., 2019, #101153} single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
+Some [@gomes2014] but not all [@epstein2018; @El-Cheikh2013] single-center observational studies examining echinocandin prophylaxis during RIC for AML have reported higher rates of breakthrough IFD in patients receiving echinocandin prophylaxis versus triazoles.
 Therefore, it is still unclear whether echinocandin prophylaxis, despite the improved safety profile when administered with SMKIs, is as effective as posaconazole prophylaxis for preventing invasive mold disease.
 
-Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast {Stanzani et al., 2019, #287617;Gomes et al., 2013, #95041; El Zein et al., 2020, #229138} and intrinsically-resistant mold such as *Fusarium* spp.
-and Mucorales compared to mould-active triazoles {Gomes et al., 2013, #95041}.
+Echinocandin prophylaxis may be associated with higher risk for breakthrough fungal infections caused by rare yeast [@stanzani_etal19; @gomes_etal14; @El2020] and intrinsically-resistant mold such as *Fusarium* spp.
+and Mucorales compared to mould-active triazoles[@Gomes2014].
 In centers or regions where these infections are more common, careful consideration should be given to early diagnosis of these breakthrough infections given their propensity for fulminant infections and rapid dissemination.
